SST_patterns

### 2020-04-20 SST_patterns.Rmd
update

# ### The temperature products
# load("~/Documents/Upwelling_MCS/Data/Final_G1SST.RData") #G1SST
# load("~/Documents/Upwelling_MCS/Data/Final.RData") # MUR
# load("~/Documents/Upwelling_MCS/Data/SACTN_US.RData") # SACTN
# load("~/Documents/Upwelling_MCS/Data/OISST_sites.RData") # OISST
# load("~/Documents/Upwelling_MCS/Data/CMC_SST.RData") # CMC temperature
```

@@

@@

@@

### The temperature products
load("~/Documents/Upwelling_MCS/Data/Final_G1SST.RData") #G1SST
load("~/Documents/Upwelling_MCS/Data/Final.RData") # MUR
load("~/Documents/Upwelling_MCS/Data/SACTN_US.RData") # SACTN
load("~/Documents/Upwelling_MCS/Data/OISST_sites.RData") # OISST
load("~/Documents/Upwelling_MCS/Data/CMC_SST.RData") # CMC temperature

@@

metric_4years <- combined_products %>% 
   filter(year(date_start) %in% 2011:2014) # only for the years 2011-2014 so 4 year period

@@

## Creating a time series graph with all of the products but showing the temperature drop but with no CMC
# X-axis: Date, Y axis: Temp

>>>>

# # ### The temperature products
# load("~/Documents/Upwelling_MCS/Data/Final_G1SST.RData") #G1SST
# load("~/Documents/Upwelling_MCS/Data/Final.RData") # MUR
# load("~/Documents/Upwelling_MCS/Data/SACTN_US.RData") # SACTN
# load("~/Documents/Upwelling_MCS/Data/OISST_fill.RData") # OISST
# load("~/Documents/Upwelling_MCS/Data/CMC_fill.RData") # CMC temperature
```

@@

```{r}
# # These following three objects (MUR, OISST, CMC) need to be the complete set of lon/lat values for your satellite data
# MUR <- MUR %>%
#   select(lon, lat) %>%
#   mutate(product = "MUR")
# 
# # Decided to work with OISST and CMC as both has a time series of 30years
OISST_prod <- OISST %>%
  dplyr::select(lon, lat) %>%
  unique() %>%
  mutate(product = "OISST")
# 
CMC_prod <- CMC %>%
  dplyr::select(lon, lat) %>%
  unique() %>%
  mutate(product = "CMC")
# 
sat_data <- rbind(CMC_prod, OISST_prod) %>% 
#   #rbind(., CMC) %>% 
dplyr::select(product, lon, lat)
# 
sat_pixels <- sat_data %>%
dplyr::select(product, lon, lat) %>%
unique()
# 
# ## For testing the nest/map pipeline
# # df <- site_pixels %>%
# #   filter(site == "Lamberts Bay") %>%
# #   select(-site)
# 
match_func <- function(df){
  df <- df %>%
    dplyr::rename(lon_site = lon, lat_site = lat)
  OISST_index <- OISST_prod[as.vector(knnx.index(as.matrix(OISST_prod[,c("lon", "lat")]),
                                                 as.matrix(df[,c("lon_site", "lat_site")]), k = 1)),] %>%
    cbind(., df)
  CMC_index <- CMC_prod[as.vector(knnx.index(as.matrix(CMC_prod[,c("lon", "lat")]),
                                             as.matrix(df[,c("lon_site", "lat_site")]), k = 1)),] %>%
    cbind(., df)
  res <- rbind(OISST_index, CMC_index)
  return(res)
}

@@

# # You may then use the 'pixel_match' object to filter out the desired pixels from the full satellite products
OISST_fill <- right_join(OISST, filter(pixel_match, product == "OISST"), by = c("lon", "lat"))
CMC_fill <- right_join(CMC, filter(pixel_match, product == "CMC"), by = c("lon", "lat"))

# #SACTN_fill <- right_join(SACTN, filter(pixel_match, product == "SACTN"), by = c("lon", "lat"))
# Clean up some RAM space
rm(OISST, CMC); gc()
# 
# # sites <- c("Port Nolloth", "Lamberts Bay", "Saldanha Bay", "Sea Point")
# # # In the SACTN dataset Hout Bay only has data until 2005. Hout Bay will now be removed from this study
# # # Hout Bay will be ignored
selected_sites <- c("Port Nolloth", "Lamberts Bay", "Sea Point", "Saldanha Bay")
# 
OISST_fill <- OISST_fill %>%
  filter(site %in% selected_sites)

CMC_fill <- CMC_fill %>%
  filter(site %in% selected_sites)

# save(OISST_fill, file = "Data/OISST_fill.RData")
# save(CMC_fill, file = "Data/CMC_fill.RData")

# # All the code below can be viewed in upwell_IDX.Rmd
# # Next to run upwelling index
# # UI Created using SAWS wind data (Find in upwell_IDX_Rmd)
# load("Data/UI_angle.RData")
# 
upwelling <- UI_angle %>%
  dplyr::rename(temp = ui.saws) %>%
  group_by(site) %>%
  # mutate(min_t = min(t),
  #        max_t = max(t)) %>%
  nest() %>% # apply the following functions to all of the variables in te dataset
  mutate(clim = purrr::map(data, ts2clm, climatologyPeriod = c("1997-01-01", "2015-12-31")), # creating a column of climatologies. Column will be named clim
         # NB: A threshold of 3 appeared to be far to strict
         # purr::map - apllies a function to each element of a vector
         exceed = purrr::map(clim, exceedance, minDuration = 1, threshold = 1)) %>%  #Upwelling cannot be descrbed as an event. Upwelling can last for a few hours. Given that we have daily data, upwelling events minimum duration here will be 1day
  # Detect consecutive days in exceedance of a given threshold.
  # mutate() %>%
  select(-data, -clim) %>%
  unnest() %>%
  filter(row_number() %% 2 == 1) %>%
  unnest() %>% # creates a column for each variables
  dplyr::rename(ui.saws = temp) %>% # rename upwelling index vale to temp so that it could work with the function
  select(site, t, ui.saws, exceedance)

@@

@@

### The temperature products
load("~/Documents/Upwelling_MCS/Data/Final_G1SST.RData") #G1SST
load("~/Documents/Upwelling_MCS/Data/Final.RData") # MUR
load("~/Documents/Upwelling_MCS/Data/SACTN_US.RData") # SACTN
load("~/Documents/Upwelling_MCS/Data/OISST_fill.RData") # OISST
load("~/Documents/Upwelling_MCS/Data/CMC_fill.RData") # CMC temperature

metric_4years <- combined_products %>% 
   filter(year(date_start) %in% 2011:2014)

@@

## Creating a time series graph with all of the products but showing the temperature drop but with no CMC
# X-axis: Date, Y axis: Temp
combined_SST <- rbind(CMC_fill,MUR_temp,G1SST_temp,OISST_temp)
